---
title: "Home"
---

The goal of this project is to analyze the relationship between test scores, IQ, and education ranking across different countries. We observe a strong positive linear association between a country's average IQ and its average test scores in math and science, indicating a perfect positive relationship. Additionally, we observe a medium positive linear relationship between a country's average test scores and its education ranking, as well as between a country's average IQ and its education ranking. It is worth noting that despite the decreasing trend of the line of best fit, countries with higher education rankings have lower values on the y-axis.

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
library(plotly)
```

```{r}
#| echo: false
#| message: false
iqData <- read_csv("data/IQRankings.csv")
rankingData <- read_csv("data/EducationRankings.csv")
scoresData <- read_csv("data/TestScoreData.csv")

rankingData <- rankingData |>
  select(country, rank2021, pop2023)

iqData <- iqData |>
  select(country, iq)

scoresData <- scoresData |>
  rename(country = Entity) |>
  rename_at(7, ~ "score") |>
  drop_na() |>
  select(country, score)

mergedData <- iqData |>
  inner_join(scoresData, by = "country") |>
  inner_join(rankingData, by = "country")
```

```{r}
#| echo: false
#| message: false
#| warning: false

model1 <- lm(rank2021 ~ score, data = mergedData)
intercept1 <- coef(model1)[1]
slope1 <- coef(model1)[2]
equation1 <- paste("Rank =", round(intercept1, 2), "+", round(slope1, 2), "* Score")
r1 <- round(cor(mergedData$rank2021, fitted(model1)), 2)

plot1 <- mergedData |>
  ggplot(aes(x = score, y = rank2021, size = pop2023, color = country)) + 
  geom_point(alpha = 0.7, aes(text = paste(country, "\n", "Score:", score, "\n", "Rank:", rank2021))) +
  geom_smooth(method = "lm", color = "orange", se = FALSE) +
  guides(color = "none", size = "none") +
  labs(
    title = "Test Scores and Education Ranking",
    subtitle = "There is a medium correlation between a country's test scores and its ranking.",
    x = "Average Test Scores in Math and Science",
    y = "Education Ranking",
    caption = "Our World in Data (2016)\nWorld Population Review (2023)"
  ) +
  annotate(
    "text",
    x = max(mergedData$score) - 35,
    y = max(mergedData$rank2021) - 1,
    label = paste(equation1, "\n                                 r =", r1)
  )

ggplotly(plot1, tooltip = "text") 
```

​

```{r}
#| echo: false
#| message: false
#| warning: false

model2 <- lm(rank2021 ~ iq, data = mergedData)
intercept2 <- coef(model2)[1]
slope2 <- coef(model2)[2]
equation2 <- paste("Rank =", round(intercept2, 2), "+", round(slope2, 2), "* IQ")
r2 <- round(cor(mergedData$rank2021, fitted(model2)), 2)

plot2 <- mergedData |>
  ggplot(aes(x = iq, y = rank2021, size = pop2023, color = country)) +
  geom_point(alpha = 0.7, aes(text = paste(country, "\n", "IQ:", iq, "\n", "Rank:", rank2021))) +
  geom_smooth(method = "lm", color = "orange", se = FALSE) +
  guides(color = "none", size = "none") +
  labs(
    title = "IQ and Education Ranking",
    subtitle = "There is a medium correlation between a country's IQ and its ranking.",
    x = "Average IQ",
    y = "Education Ranking",
    caption = "World Population Review (2023)"
  ) +
  annotate(
    "text", 
    x = max(mergedData$iq) - 6, 
    y = max(mergedData$rank2021) - 1,
    label = paste(equation2, "\n                            r =", r2),
  )

ggplotly(plot2, tooltip = "text")
```

​

```{r}
#| echo: false
#| message: false
#| warning: false

model3 <- lm(iq ~ score, data = mergedData)
intercept3 <- coef(model3)[1]
slope3 <- coef(model3)[2]
equation3 <- paste("Score =", round(intercept3, 2), "+", round(slope3, 2), "* IQ")
r3 <- round(cor(mergedData$score, fitted(model3)), 2)

plot3 <- mergedData |>
  ggplot(aes(x = iq, y = score, size = pop2023, color = country)) +
  geom_point(alpha = 0.7, aes(text = paste(country, "\n", "Score:", score, "\n", "IQ:", iq))) +
  geom_smooth(method = "lm", color = "orange", se = FALSE) +
  guides(color = "none", size = "none") +
  labs(
    title = "IQ and Test Scores",
    subtitle = "IQ and test scores are almost perfectly correlated.",
    x = "Average IQ",
    y = "Average Test Scores in Math and Science",
    caption = "Our World in Data (2016)\nWorld Population Review (2023)"
  ) +
  annotate(
    "text", 
    x = max(mergedData$iq) - 5, 
    y = min(mergedData$score) + 5,
    label = paste(equation3, "\n                               r =", r3),
  )

ggplotly(plot3, tooltip = "text")
```
